The \dealii{} Library, Version 8.5

### 2017-03-21 8.5/paper.tex
Move the discussion of the code gallery.

\item New tutorial programs step-55, step-56, and step-57; as well as
  updates to step-27, step-37, and step-44.

\item New code gallery programs demonstrating
\marginpar{Isn't the code gallery itself new for 8.5?}
  \begin{enumerate}
    \item[(i)] quasi-static visco-elastic material behavior,
    \item[(ii)] multiphase Navier-Stokes flow,
    \item[(iii)] the evolution of global-scale topography on planetary bodies,
    \item[(iv)] goal-oriented elastoplasticity.
  \end{enumerate}

@@

>>>>

\item New tutorial programs step-55, step-56, and step-57; as well as
  updates to step-27, step-37, and step-44. In addition, the separate code
  gallery of \dealii{} has gained a number of new entries.

@@

In addition to tutorials, \dealii{} has a separate ``code gallery'' that
consists of programs shared by users as examples of what can be
done with \dealii{}. While not part of the release process, it is nonetheless
worth mentioning that the set of new programs since the last release covers
the following topics:
\marginpar{Add the muscle elasticity example if it is merged in time.}
  \begin{itemize}
    \item Auasi-static visco-elastic material behavior;
    \item Multiphase Navier-Stokes flow;
    \item The evolution of global-scale topography on planetary bodies;
    \item Goal-oriented elastoplasticity.
  \end{itemize}
